Mental Health Factors and Covid

### 2025-04-20 code/analysis-code/analysis.qmd
Part 5 analysis

To start, I'll load packages. As I need packages along the way, I'll return here and add them.
```{r}
library(tidyverse)
library(survey)
library(tableone)
library(gt)
library(here)
```

Now, loading data using the here package.
```{r}
here() #set working directory
data <- readRDS(here("data","processed-data", "data3.rds"))
data <- labelled::remove_val_labels(data) #removes labels from haven package which cause problems
```

@@

@@

>>>>

To start, I'll load packages. As I need packages along the way, I'll return here and add them.
```{r}
library(tidyverse)
library(survey)
library(tableone)
library(mice)
library(mitools)
library(miceadds)
library(tidymodels)
library(caret)
library(gt)
library(here)
```

Now, loading data using the here package.
```{r}
here() #set working directory
#data <- readRDS(here("data","processed-data", "data3.rds"))
#data <- labelled::remove_val_labels(data) #removes labels from haven package which cause problems

data_imputed <- readRDS(here("data","processed-data", "binary_imputed_datasets.rds"))
```

@@

We create estimates and CIs using complex survery design variables, using the multiple imputed data.

```{r}

# Create survey design objects for each transformed dataset
svy_designs <- lapply(data_imputed, function(data) {
  svydesign(ids = ~PSU, strata = ~STRATA, weights = ~SAMPWEIGHT, data = data , nest=TRUE)
})

# Function to get complete estimates (both 0 and 1) stratified by COVID status
get_complete_stratified_estimates <- function(var_name) {
  results <- data.frame(
    Variable = character(),
    COVID_Status = character(),
    Binary_Value = numeric(),
    Estimate = numeric(),
    CI_lower = numeric(),
    CI_upper = numeric(),
    stringsAsFactors = FALSE
  )

  # Loop through COVID status (0 and 1)
  for (covid_val in c(0, 1)) {
    covid_label <- ifelse(covid_val == 0, "Negative", "Positive")

    # Calculate proportions for this COVID status
    props <- lapply(svy_designs, function(design) {
      # Create a subset design
      subdesign <- subset(design, COVID == covid_val)
      # Create formula for the variable
      formula <- as.formula(paste0("~factor(", var_name, ")"))
      # Calculate proportions
      svymean(formula, subdesign, na.rm = TRUE)
    })

    # Pool results
    pooled <- MIcombine(props)

    # Extract results for both binary values (if available)
    coef_names <- names(coef(pooled))

    # Handle different potential naming patterns
    for (bin_val in c(0, 1)) {
      # Check different possible coefficient names
      possible_names <- c(
        paste0("factor(", var_name, ")", bin_val),
        as.character(bin_val)
      )

      # Find the matching coefficient name
      coef_idx <- NULL
      for (name in possible_names) {
        if (name %in% coef_names) {
          coef_idx <- which(coef_names == name)
          break
        }
      }

      # If found, extract estimates
      if (!is.null(coef_idx)) {
        est <- coef(pooled)[coef_idx]
        ci <- confint(pooled)[coef_idx, ]

        # Add to results
        results <- rbind(results, data.frame(
          Variable = var_name,
          COVID_Status = covid_label,
          Binary_Value = bin_val,
          Estimate = round(est * 100, 1),
          CI_lower = round(ci[1] * 100, 1),
          CI_upper = round(ci[2] * 100, 1)
        ))
      }
    }
  }

  return(results)
}

# Variables to analyze
variables <- c("EXERCISE", "SLEEP", "DEPRESSED", "TROUBLE_SLEEPING", "SOCIAL")

# Get complete stratified estimates for each variable
complete_results <- lapply(variables, get_complete_stratified_estimates)

# Combine results into a single data frame
complete_df <- do.call(rbind, complete_results)

# Reshape for better presentation
formatted_results <- complete_df %>%
  mutate(Binary_Label = ifelse(Binary_Value == 1, "Yes", "No")) %>%
  select(Variable, COVID_Status, Binary_Label, Estimate, CI_lower, CI_upper) %>%
  arrange(Variable, COVID_Status, desc(Binary_Label))

print(formatted_results)

Now let's turn that into a nice table using GT, and I'll save it to use in the manuscript later. 
```{r}
#checking
summary(formatted_results)
str(formatted_results)
names(formatted_results)

# Prepare the data by combining Variable and Binary_Label, pivoting, and formatting the results
table1_imputed <- formatted_results %>%
  mutate(Binary_Label = ifelse(Binary_Label == "Yes", 1, 0),  # Convert Yes to 1 and No to 0
         Variable_Label = paste(Variable, Binary_Label, sep = " = ")) %>%
  pivot_wider(
    names_from = COVID_Status,
    values_from = c(Estimate, CI_lower, CI_upper),
    names_glue = "{COVID_Status}_{.value}"
  ) %>%
  mutate(
    # Scale the estimates and CI by 0.01
    Estimate_Negative = Negative_Estimate * 0.01,
    CI_Negative = sprintf("(%.2f, %.2f)", Negative_CI_lower * 0.01, Negative_CI_upper * 0.01),
    Estimate_Positive = Positive_Estimate * 0.01,
    CI_Positive = sprintf("(%.2f, %.2f)", Positive_CI_lower * 0.01, Positive_CI_upper * 0.01)
  ) %>%
  select(Variable_Label, Estimate_Negative, CI_Negative, Estimate_Positive, CI_Positive) %>%
  gt() %>%
  tab_header(
    title = "Estimated proportions of mental health related factors by COVID test status"
  ) %>%
  tab_spanner(
    label = "COVID Negative",
    columns = c(Estimate_Negative, CI_Negative)
  ) %>%
  tab_spanner(
    label = "COVID Positive",
    columns = c(Estimate_Positive, CI_Positive)
  ) %>%
  cols_label(
    Variable_Label = "Variable",               # Rename Variable_Label to Variable
    Estimate_Negative = "Estimate",            # Rename Estimate_Negative to Estimate
    CI_Negative = "95% CI",                    # Rename CI_Negative to 95% CI
    Estimate_Positive = "Estimate",            # Rename Estimate_Positive to Estimate
    CI_Positive = "95% CI"                     # Rename CI_Positive to 95% CI
  )

# Save the table as a PNG
here()
gtsave(table1_imputed, here("results", "figures", "table1_imputed.png"))
```
################################################################################
Now, we will start modeling COVID postivity as an outcome of mental health factors.

Up first, we will create singleton models to individually study the effects of mental health factors on covid test positivity status.

```{r}
# Create a survey design object for each completed dataset
survey_designs <- lapply(data_imputed, function(data_i) {
  svydesign(
    id = ~PSU,
    strata = ~STRATA,
    weights = ~SAMPWEIGHT,
    nest = TRUE,
    data = data_i
  )
})

# Fit svyglm models for EXERCISE predictor
models_exercise <- lapply(survey_designs, function(dsgn) {
  svyglm(COVID ~ EXERCISE, design = dsgn, family = quasibinomial())
})

# Extract coefficients and standard errors for each model
model_exercise_coef <- lapply(models_exercise, function(model) {
  data.frame(
    Estimate = coef(model),
    Std.Error = sqrt(diag(vcov(model))),
    stringsAsFactors = FALSE
  )
})

# Calculate means and variances for pooling
estimates <- do.call(rbind, lapply(model_exercise_coef, function(x) x$Estimate))
se <- do.call(rbind, lapply(model_exercise_coef, function(x) x$Std.Error))

# Compute the mean across imputations
mean_estimate <- apply(estimates, 2, mean)

# Compute within-imputation variance (average variance across imputations)
within_variance <- apply(se^2, 2, mean)

# Compute between-imputation variance (variance of the estimates across imputations)
between_variance <- apply(estimates, 2, var)

# Calculate the total variance using Rubin's rule
total_variance <- within_variance + (1 + 1 / length(survey_designs)) * between_variance

# Calculate the pooled standard error
pooled_se <- sqrt(total_variance)

# Calculate the 95% confidence intervals
ci_low <- mean_estimate - 1.96 * pooled_se
ci_high <- mean_estimate + 1.96 * pooled_se

# Create a data frame with pooled estimates, standard errors, and confidence intervals
pooled_exercise <- data.frame(
  Estimate = mean_estimate,
  Std.Error = pooled_se,
  CI_Low = ci_low,
  CI_High = ci_high
)

# Display the pooled results
pooled_exercise

library(survey)

# Fit svyglm models for EXERCISE predictor (and other predictors if needed)
predictors <- c("EXERCISE", "DEPRESSED", "SLEEP", "TROUBLE_SLEEPING", "SOCIAL")

# Fit models for each predictor
models <- lapply(predictors, function(predictor) {
  lapply(survey_designs, function(dsgn) {
    formula <- as.formula(paste("COVID ~", predictor))
    svyglm(formula, design = dsgn, family = quasibinomial())
  })
})

# Extract coefficients and standard errors for each model
model_coef <- mapply(function(predictor, predictor_models) {
  lapply(predictor_models, function(model) {
    data.frame(
      Estimate = coef(model),
      Std.Error = sqrt(diag(vcov(model))),
      stringsAsFactors = FALSE
    )
  })
}, predictors, models, SIMPLIFY = FALSE)

# Calculate means, variances, and p-values for pooling
pooled_results <- lapply(names(model_coef), function(predictor_name) {
  coefs <- model_coef[[predictor_name]]

  estimates <- do.call(rbind, lapply(coefs, function(x) x$Estimate))
  se <- do.call(rbind, lapply(coefs, function(x) x$Std.Error))

  # Compute the mean across imputations
  mean_estimate <- apply(estimates, 2, mean)

  # Compute within-imputation variance (average variance across imputations)
  within_variance <- apply(se^2, 2, mean)

  # Compute between-imputation variance (variance of the estimates across imputations)
  between_variance <- apply(estimates, 2, var)

  # Calculate the total variance using Rubin's rule
  total_variance <- within_variance + (1 + 1 / length(survey_designs)) * between_variance

  # Calculate the pooled standard error
  pooled_se <- sqrt(total_variance)

  # Calculate the 95% confidence intervals
  ci_low <- mean_estimate - 1.96 * pooled_se
  ci_high <- mean_estimate + 1.96 * pooled_se

  # Calculate z-statistics and p-values
  z_stat <- mean_estimate / pooled_se
  p_values <- 2 * (1 - pnorm(abs(z_stat)))  # Two-tailed p-value

  # Exponentiate to get Odds Ratios (ORs) from log-odds
  or_estimate <- exp(mean_estimate)
  ci_low_or <- exp(ci_low)
  ci_high_or <- exp(ci_high)

  # Create a data frame with pooled Odds Ratios, standard errors, confidence intervals, and p-values
  data.frame(
    Predictor = rep(predictor_name, length(mean_estimate)),
    OR = or_estimate,
    Std.Error = pooled_se,
    CI_Low = ci_low_or,
    CI_High = ci_high_or,
    p_value = p_values,
    row.names = names(mean_estimate)
  )
})

# Combine results for all predictors into one data frame
pooled_exercise <- do.call(rbind, pooled_results)

# Display the labeled pooled results
pooled_exercise

Now we will make a nice table of that using gt.

```{r}
names(pooled_exercise)
str(pooled_exercise)

#not including intercepts values
# Assuming 'pooled_exercise' is your data frame
pooled_exercise %>%
  group_by(Predictor) %>%
  slice(2) %>%  # Select only the second row for each Predictor
  ungroup() %>%
  mutate(CI = paste0("(", round(CI_Low, 3), ", ", round(CI_High, 3), ")")) %>%
  select(Predictor, OR, CI, p_value) %>%
  gt() %>%
  tab_header(
    title = "Associations of individual mental health factors with positive covid test result"
  ) %>%
  cols_label(
    Predictor = "Predictor",
    OR = "Odds Ratio",
    CI = "Confidence Interval",
    p_value = "P-Value"
  ) %>%
  fmt_number(
    columns = vars(OR, p_value),
    decimals = 3
  )

################################################################################
This is the part of the project in which I demonstrate complex techniques learned during this class.

Next, we will make the multivariate model. I will use cross validation for this. The RMSE is found to be 0.4450602.
```{r}

cross_validation_imputed_rmse <- function(imputed_data, design, predictors, k_folds = 5) {
  rmse_list <- numeric(length(imputed_data))  # Store RMSE for each imputation

  for (i in 1:length(imputed_data)) {
    data <- imputed_data[[i]]
    set.seed(123)
    folds <- sample(1:k_folds, size = nrow(data), replace = TRUE)

    fold_rmse <- numeric(k_folds)  # RMSE for each fold

    for (fold in 1:k_folds) {
      train_data <- data[folds != fold, ]
      test_data  <- data[folds == fold, ]

      # Survey design for training and testing
      train_design <- svydesign(ids = ~1, data = train_data, weights = ~SAMPWEIGHT)
      formula <- as.formula(paste("COVID ~", paste(predictors, collapse = " + ")))
      model <- svyglm(formula, design = train_design, family = quasibinomial())

      # Predictions
      predictions <- predict(model, newdata = test_data, type = "response")
      actual <- test_data$COVID

      # Compute RMSE for this fold
      fold_rmse[fold] <- sqrt(mean((predictions - actual)^2, na.rm = TRUE))
    }

    # Average RMSE over folds for this imputed dataset
    rmse_list[i] <- mean(fold_rmse)
  }

  # Average RMSE over all imputed datasets
  overall_rmse <- mean(rmse_list)

  return(list(rmse_per_imputation = rmse_list, overall_rmse = overall_rmse))
}

# Assuming you have your imputed_data and a vector of predictors
results <- cross_validation_imputed_rmse(imputed_data = data_imputed,
                                         design = NULL,  # Not used inside, can be omitted
                                         predictors = c("AGE", "SLEEP", "DEPRESSED"))

# View results
results$rmse_per_imputation  # RMSE for each imputed dataset
results$overall_rmse         # Average RMSE across imputations
```

Now, we will make a LASSO regression model. For this, I'm not going to use the multiple imputation dataset. I'm just going to pick a sinlge imputed dataset, the first one. The RMSE is 0.276.

```{r}
# Extract the first completed imputed dataset
data1 <- data_imputed[[1]]  # You can loop over 1:5 later

# Then define the survey design
survey_design <- svydesign(
  ids = ~PSU,
  strata = ~STRATA,
  weights = ~SAMPWEIGHT,
  data = data1,
  nest=TRUE
)

set.seed(1234)  # for reproducibility

# Choose your outcome and predictors
outcome_var <- "DEPRESSED"
predictor_vars <- c("EXERCISE", "SLEEP", "DEPRESSED", "TROUBLE_SLEEPING", "SOCIAL")

# Loop over imputations and compute RMSE
rmse_list <- map(data_imputed, function(dat) {
  # Drop missing in predictors or outcome if any slipped through
  dat <- dat %>% drop_na(all_of(c(outcome_var, predictor_vars, "SAMPWEIGHT")))

  # Create design matrix X and response y
  X <- model.matrix(as.formula(paste(outcome_var, "~", paste(predictor_vars, collapse = "+"))), dat)[, -1]
  y <- dat[[outcome_var]]
  w <- dat$SAMPWEIGHT

  # Split into training and test sets (e.g., 70/30 split)
  train_idx <- sample(seq_len(nrow(X)), size = 0.7 * nrow(X))
  test_idx <- setdiff(seq_len(nrow(X)), train_idx)

  X_train <- X[train_idx, ]
  y_train <- y[train_idx]
  w_train <- w[train_idx]

  X_test <- X[test_idx, ]
  y_test <- y[test_idx]
  w_test <- w[test_idx]

  # Fit weighted lasso model
  cv_fit <- cv.glmnet(
    x = X_train,
    y = y_train,
    alpha = 1,
    weights = w_train,
    family = "binomial",  # change to "binomial" for binary outcome
    nfolds = 5
  )

  # Predict on test set
  preds <- predict(cv_fit, newx = X_test, s = "lambda.min")

  # Weighted RMSE
  sqrt(weighted.mean((y_test - preds)^2, w_test))
})

# Pool RMSE across imputations
pooled_rmse <- mean(unlist(rmse_list))

# Output
cat("RMSE for each imputation:\n")
print(unlist(rmse_list))
cat("\nPooled RMSE across imputations:", round(pooled_rmse, 3), "\n")

################################################################################
The following code was used prior to development of imputed data and is no longer relevant. It may be ignored. I am keeping it in case it serves as a useful reference for the rest of the project or future endeavors.
################################################################################

@@

################################################################################

Up next, we will run the singleton models. For these, our outcome variable (covid test result) will be used as a variable for each of the respective predictor vairbales that we created in the processing code. These models appear as the following:

$$ Y_{CovidPositive} = \beta_0 + \beta_1 \cdot X_{Exercise} $$
$$ Y_{CovidPositive} = \beta_0 + \beta_1 \cdot X_{Sleep} $$
$$ Y_{CovidPositive} = \beta_0 + \beta_1 \cdot X_{Depressed} $$
$$ Y_{CovidPositive} = \beta_0 + \beta_1 \cdot X_{TroubleSleeping} $$
$$ Y_{CovidPositive} = \beta_0 + \beta_1 \cdot X_{Social} $$
Create survey design.
```{r}
#review names to use below
names(data)

#create survey object using design variables
survey_design <- svydesign(
  ids = ~PSU,
  strata = ~STRATA,
  weights = ~SAMPWEIGHT,
  data = data,
  nest = TRUE
)

pr_results <- data.frame()

variables <- c("EXERCISE", "SLEEP", "DEPRESSED", "TROUBLE_SLEEPING", 
               "SOCIAL")

for (var in variables) {
  # Create the formula dynamically
  formula <- as.formula(paste("COVID ~", var))

  # Fit the model
  model <- svyglm(
    formula, 
    design = survey_design, 
    family = quasibinomial(link = "log")
  )

  # Extract prevalence ratios and confidence intervals
  pr <- exp(coef(model))  # Prevalence ratios
  pr_ci <- exp(confint(model))  # Confidence intervals

  # Extract p-values
  p_values <- summary(model)$coefficients[, "Pr(>|t|)"]

  # Combine results into a single table
  pr_results <- rbind(
    pr_results,
    data.frame(
      Variable = var,
      Estimate = pr[-1],  # Skip the intercept
      `2.5% CI` = pr_ci[-1, 1],
      `97.5% CI` = pr_ci[-1, 2],
      `p-value` = p_values[-1]  # Skip the intercept
    )
  )
}

# Print the results
print(pr_results)

Now, we will make that into a nice quality table using the gt package and the help of chatGPT and Claude.
```{r}
#checking
glimpse(pr_results)
str(pr_results)

#create the gt table
pr_results %>%
  mutate(
    Predictor = stringr::str_to_title(gsub("_", " ", Variable)),
    `Prevalence Ratio` = round(Estimate, 2),
    `95% CI` = paste0("(", round(X2.5..CI, 2), ", ", round(X97.5..CI, 2), ")"),
    `p-value` = format.pval(p.value, digits = 3, eps = .001)
  ) %>%
  select(Predictor, `Prevalence Ratio`, `95% CI`, `p-value`) %>%
  gt() %>%
  tab_header(
    title = md("**Positive COVID Test Result Association with Mental Health Factors**")
  ) %>%
  tab_options(
    column_labels.border.bottom.width = px(1.5),  # Bold line under column headers
    column_labels.border.bottom.color = "black"
  )

Now, we're going to complete the process of model selection, using backwards selection. We want to end up with a model we can use for prediction purposes. Our initial model looks like this: 
$$ Y_{CovidPositive} = \beta_0 + \beta_1 \cdot X_{Exercise} + \beta_2 \cdot X_{Sleep} + \beta_3 \cdot X_{Depressed} + \beta_4 \cdot X_{TroubleSleeping} + \beta_5 \cdot X_{Social} $$
Let's find the AIC value. 
```{r}

unique(data$COVID)
model_full <- svyglm(
  COVID ~ EXERCISE + SLEEP + DEPRESSED + TROUBLE_SLEEPING + SOCIAL,
  design = survey_design,
  family = quasibinomial(link = "log")
)
# Perform backward selection based on AIC
model_step <- step(model_full, direction = "backward", trace = 1)
summary(model_step)

### 2025-04-20 code/eda-code/eda.qmd
Part 5 analysis

---
title: "Data-Cleaning"
---

To start, I'll load packages. As I need packages along the way, I'll return here and add them.
```{r}
library(tidyverse)
library(gt)
library(webshot2)
library(here)
```

Now, loading data using the here package.
```{r}
here() #set working directory
data <- readRDS(here("data","processed-data", "data3.rds"))
```

@@

>>>>

---
title: "Exploratory Data Analysis"
---

To start, I'll load packages. As I need packages along the way, I'll return here and add them.
```{r}
library(tidyverse)
library(gt)
library(webshot2)
library(survey)
library(mice)
library(CreateTableOne)
library(here)
```

Now, loading data using the here package.
```{r}
here() #set working directory
data <- readRDS(here("data","processed-data", "data3.rds"))
data <- labelled::remove_val_labels(data) #removes labels from haven package which cause problems
```

@@

Now, let's examine the imputed datasets to ensure they're not containing NAs. I'm only going to display this for one of them, given they were all created the same way, checking one will be adequate.
```{r}
#read it in
here()
data_imputed <- readRDS(here("data", "processed-data", "binary_imputed_datasets.rds"))

# Use the first completed dataset from the list
data_imputed_df1 <- data_imputed[[1]]

#select variables we want
vars <- c("EXERCISE", "SLEEP", "DEPRESSED", "TROUBLE_SLEEPING", "SOCIAL", "COVID")

#reshape data
long_data <- data_imputed_df1 %>%
  select(all_of(vars)) %>%
  pivot_longer(cols = everything(), names_to = "variable", values_to = "value") %>%
  filter(!is.na(value))

# Create histograms
ggplot(long_data, aes(x = value)) +
  geom_histogram(bins = 30, color = "black", fill = "skyblue") +
  facet_wrap(~ variable, scales = "free") +   # Facet by variable for separate histograms
  theme_minimal() +
  labs(title = "Histograms of Imputed Variables", x = "Value", y = "Frequency")

#checking that there's no NA's in the data
na_count <- colSums(is.na(long_data))
na_count
```

### 2025-04-20 code/processing-code/processing.qmd
Part 5 analysis

To start, I'll load packages. As I need packages along the way, I'll return here and add them.
```{r}
library(tidyverse)
library(gt)
library(webshot2)
library(here)
```

@@

>>>>

To start, I'll load packages. As I need packages along the way, I'll return here and add them.
```{r}
library(tidyverse)
library(gt)
library(webshot2)
library(survey)
library(mice)
library(tableone) #added from part 3 feedback
library(mitools)
library(here)
```

@@

After completed EDA, there's significant missingness in the data. At the recommendation of my peers, I will use multiple imputation, creating 5 sets of imputed data. I re-create the binary variables in each of the 5 imputed datasets, then save to use in the EDA file. 
```{r}
# First, let's set up the imputation
# Create a subset of variables for imputation
data1 <- labelled::remove_val_labels(data_original) #removes labels from haven package which cause problems
imputation_vars <- c("AGE", "PA18AERSTR", "HRSLEEP", "DEPFREQ", 
                     "PHQSLEEP", "CMPSUPPORT", "CVDTESTRSLT", 
                     "STRATA", "PSU", "SAMPWEIGHT")

# Create a subset of your data with just these variables
data_imp <- data1[, imputation_vars]

# Examine the missing data pattern
md.pattern(data_imp)

# Initialize the imputation - including survey design variables in the imputation model
# but not imputing them
imp <- mice(data_imp, maxit = 0)

# Customize the predictor matrix to account for complex survey design
pred <- imp$predictorMatrix
pred[c("STRATA", "PSU", "SAMPWEIGHT"), ] <- 0  # Don't use these as outcomes
pred[, c("STRATA", "PSU", "SAMPWEIGHT")] <- 1  # Use these as predictors

# Customize the method - ensure we don't impute design variables
meth <- imp$method
meth[c("STRATA", "PSU", "SAMPWEIGHT")] <- ""

# Run multiple imputation with 5 imputations (increase m for better estimates)
imp_data <- mice(data_imp, m = 5, predictorMatrix = pred, method = meth, maxit = 5)

# Check convergence
plot(imp_data)

# Get a single completed dataset (for example, the first one)
completed_data1 <- complete(imp_data, 1)

# For analysis with complex survey design
# Create a survey design object with the imputed data
# Repeat for each imputed dataset and pool results

# Get all 5 imputed datasets
imputed_datasets <- lapply(1:5, function(i) complete(imp_data, i))

# Create a function to transform variables into binary using your specific rules
create_binary_vars <- function(df) {
  # Clean AGE and PA18AERSTR
  df$AGE[df$AGE %in% c(997, 999)] <- NA
  df$PA18AERSTR[df$PA18AERSTR %in% c(0, 7, 8, 9)] <- NA

  # EXERCISE
  df$EXERCISE <- ifelse(df$PA18AERSTR %in% c(2, 3, 4), 1,
                        ifelse(is.na(df$PA18AERSTR), NA, 0))

  # SLEEP
  df$SLEEP <- NA_real_
  df$SLEEP[which(df$AGE < 1)] <- ifelse(df$HRSLEEP[which(df$AGE < 1)] >= 12 &
                                          df$HRSLEEP[which(df$AGE < 1)] <= 16, 1, 0)
  df$SLEEP[which(df$AGE >= 1 & df$AGE < 3)] <- ifelse(df$HRSLEEP[which(df$AGE >= 1 & df$AGE < 3)] >= 11 &
                                                       df$HRSLEEP[which(df$AGE >= 1 & df$AGE < 3)] <= 14, 1, 0)
  df$SLEEP[which(df$AGE >= 3 & df$AGE < 6)] <- ifelse(df$HRSLEEP[which(df$AGE >= 3 & df$AGE < 6)] >= 10 &
                                                       df$HRSLEEP[which(df$AGE >= 3 & df$AGE < 6)] <= 13, 1, 0)
  df$SLEEP[which(df$AGE >= 6 & df$AGE < 13)] <- ifelse(df$HRSLEEP[which(df$AGE >= 6 & df$AGE < 13)] >= 9 &
                                                        df$HRSLEEP[which(df$AGE >= 6 & df$AGE < 13)] <= 12, 1, 0)
  df$SLEEP[which(df$AGE >= 13 & df$AGE <= 18)] <- ifelse(df$HRSLEEP[which(df$AGE >= 13 & df$AGE <= 18)] >= 8 &
                                                           df$HRSLEEP[which(df$AGE >= 13 & df$AGE <= 18)] <= 10, 1, 0)

  # DEPRESSED
  df$DEPRESSED <- NA_real_
  df$DEPRESSED[df$DEPFREQ %in% c(1, 2)] <- 1
  df$DEPRESSED[df$DEPFREQ %in% c(3, 4, 5)] <- 0
  df$DEPRESSED[df$DEPFREQ %in% c(0, 7, 8, 9)] <- NA

  # TROUBLE_SLEEPING
  df$TROUBLE_SLEEPING <- NA_real_
  df$TROUBLE_SLEEPING[df$PHQSLEEP %in% c(1, 2, 3)] <- 1
  df$TROUBLE_SLEEPING[df$PHQSLEEP == 0] <- 0
  df$TROUBLE_SLEEPING[df$PHQSLEEP %in% c(6, 7, 8, 9)] <- NA

  # SOCIAL
  df$SOCIAL <- NA_real_
  df$SOCIAL[df$CMPSUPPORT == 1] <- 0
  df$SOCIAL[df$CMPSUPPORT == 2] <- 1
  df$SOCIAL[df$CMPSUPPORT == 3] <- 0
  df$SOCIAL[df$CMPSUPPORT %in% c(0, 7, 8, 9)] <- NA

  # COVID
  df$COVID <- NA_real_
  df$COVID[df$CVDTESTRSLT == 2] <- 1
  df$COVID[df$CVDTESTRSLT == 1] <- 0
  df$COVID[df$CVDTESTRSLT %in% c(0, 3, 7, 8, 9)] <- NA

  return(df)
}

# Apply transformation to each imputed dataset
binary_imputed_datasets <- lapply(imputed_datasets, create_binary_vars)

glimpse(binary_imputed_datasets)

#save for later
here()
saveRDS(binary_imputed_datasets, file = here("data", "processed-data", "binary_imputed_datasets.rds"))
```

### 2025-04-20 products/manuscript/Manuscript.qmd
Part 5 analysis

```{r, echo=FALSE, message=FALSE}
# load a few R packages
library(here)
library(knitr)
library(tidyverse)
library(tableone)
library(survey)
library(gt)
here()
```

>>>>

```{r, echo=FALSE, message=FALSE}
# load a few R packages
library(here)
library(knitr)
library(tidyverse)
library(mice)
library(miceadds)
library(mitools)
library(tableone)
library(survey)
library(gt)
here()
```
